Binary companions of evolved stars in \apogee\ \DR: \\ Search method and catalog of $\sim$5,000 companions

### 2018-04-02 paper/1-catalog/twoface-catalog.tex
refs and update unimodal table
Coauthors

\author{APOGEE Team}

@@

It is a pleasure to thank Keith Hawkins (Columbia), Yuan-Sen Ting (Princeton),
\todo{who else?}.

>>>>

% APOGEE RV var co-authors
\author{Nathan De Lee}
\affiliation{Department of Physics and Astronomy, Vanderbilt University, VU Station 1807, Nashville, TN 37235, USA}

\author{Steven R. Majewski}
\affiliation{Department of Astronomy, University of Virginia, Charlottesville, VA 22904-4325, USA}

\author{David L. Nidever}
\affiliation{Department of Physics, Montana State University, P.O. Box
173840, Bozeman, MT 59717-3840}
\affiliation{National Optical Astronomy Observatory, 950 North Cherry
Ave, Tucson, AZ 85719}

\author{Nicholas Troup}
\affiliation{}

% Other APOGEE co-authors:
\author{Jos\'e G. Fern\'andez-Trincado}
\affiliation{Departamento de Astronom\'ia, Universidad de Concepci\'on, Casilla 160-C, Concepci\'on, Chile}

\author{Domingo An\'ibal Garc\'ia-Hern\'andez}
\affiliation{Instituto de Astrof\'isica de Canarias, 38205 La Laguna, Tenerife, Spain}

\author{Pen\'elope Longa-Pe\~na}
\affiliation{Unidad de Astronom\'ia, Universidad de Antofagasta, Avenida Angamos 601, Antofagasta 1270300, Chile}

\author{Christian Nitschelm}
\affiliation{Unidad de Astronom\'ia, Universidad de Antofagasta, Avenida Angamos 601, Antofagasta 1270300, Chile}

\author{Olga Zamora}
\affiliation{Instituto de Astrof\'isica de Canarias, 38205 La Laguna, Tenerife, Spain}

@@

It is a pleasure to thank
Kevin Covey (WWU),
Marina Kounkel (WWU),
Keith Hawkins (Columbia),
Melissa Ness (Columbia/Flatiron),
David Spergel (Princeton/Flatiron),
and Yuan-Sen Ting (Princeton).
